SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source Term Evaluation

### 2018-03-05 paper.tex
update

As the importance of detailed chemical kinetics for predictive reactive-flow simulations has become recognized~\cref{LU2009192}, the size and complexity of chemical kinetic models describing current and next-generation fuels relevant to transportation and power generation have increased greatly; e.g., a recent biodiesel model consists of \textasciitilde\num{3500} chemical species, and over \num{17000} reactions.
Moreover, the cost of evaluating the chemical source terms scales linearly with the size of the model, while evaluation and factorization of the chemical kinetic Jacobian, if naively implemented, scale quadratically and cubically with the number of species in the model~\cref{LU2009192}.
These factors often make the use of detailed chemical kinetics prohibitive in practice; for direct numerical simulations, evaluation of reaction rates can consume around half of the total runtime~\cite{Spafford:2010aa}.
In addition, chemical kinetic Jacobian evaluation and factorization---required for most implicit integration techniques utilized to deal with numerical stiffness---becomes a bottleneck for even modestly sized chemical models in realistic reactive flow simulations~\cite{LU2009192}, and necessitates use of other cost-reduction strategies.

>>>>

As the importance of detailed chemical kinetics for predictive reactive-flow simulations has become recognized~\cite{LU2009192}, the size and complexity of chemical kinetic models describing current and next-generation fuels relevant to transportation and power generation have increased greatly; e.g., a recent biodiesel model consists of \textasciitilde\num{3500} chemical species, and over \num{17000} reactions.
Moreover, the cost of evaluating the chemical source terms scales linearly with the size of the model, while evaluation and factorization of the chemical kinetic Jacobian, if naively implemented, scale quadratically and cubically with the number of species in the model~\cite{LU2009192}.
These factors often make the use of detailed chemical kinetics prohibitive in practice; for direct numerical simulations, evaluation of reaction rates can consume around half of the total runtime~\cite{Spafford:2010aa}.
In addition, chemical kinetic Jacobian evaluation and factorization---required for most common implicit integration techniques utilized to deal with numerical stiffness---becomes a bottleneck for even modestly-sized chemical models in realistic reactive flow simulations, and necessitates use of other cost-reduction strategies~\cite{LU2009192}.
